---
output:
  md_document:
    variant: markdown_github
---

# About packageForGapminder

`packageForGapminder` is a package which makes model pop/lifeExp/gdpPercap VS year for countries in gapminder dataset easier, as well as makes it possible to use only one line code to help you get a intuitive view on how well pop/lifeExp/gdpPercap and year in gapminder dataset fits a linear model. All functions here are based on my [homework4](https://github.com/STAT545-UBC/lina_qiu/blob/master/STAT545/Homework04/Homework04.md) for STAT545.

To install the package:

```{r installation, eval=FALSE}
##Make sure you load devtools package first
library(devtools)
##Install packageForGapminder
devtools::install_github("LinaQiu/packageForGapminder")
```

Load packages here:
```{r}
library(packageForGapminder) 
library(knitr)
options(knitr.table.format="markdown")        #Set the format for tables as "markdown"
```

In this package, we have three functions in total. See below.

* `gapminder_lmfit()`: Fit a linear model to pop/lifeExp/gdpPercap VS year for a country in gapminder dataset. 

* `gapminder_lm_table()`: Create a table for fitted linear model between variables pop/lifeExp/gdpPercap and year in gapminder dataset.

* `gapminder_lm_plot()`:Draw a plot to show how well pop/lifeExp/gdpPercap and year in gapminder dataset fits a linear model.

Besides, by default, all these three funtions will fit the linear model to data `pop` VS `year` for a gapminder country.

# Using `gapminder_lmfit()`:
Fit linear model to gapminder country data.

```{r}
gapminder_lmfit("Canada")                   ##fit a linear model to pop VS year for "Canada"
gapminder_lmfit("Canada","year","lifeExp")  ##fit a linear model to lifeExp VS year for "Canada"
gapminder_lmfit("China","year","gdpPercap") ##fit a linear model to gdpPercap VS year for "China"
```

# Using `gapminder_lm_table()`:
Get the table which compares the actual pop/lifeExp/gdpPercap values with the predicted values that we compute from the linear model.

```{r}
table1 <- gapminder_lm_table("Canada")
kable(table1)
table2 <- gapminder_lm_table("Canada","year","lifeExp")
kable(table2)
table3 <- gapminder_lm_table("China","year","gdpPercap")
kable(table3)
```

# Using `gapminder_lm_plot()`:
Draw a plot to give you an intuitive view on how well a gapminder country data(pop/lifeExp/gdpPercap VS year) fits a linear model.

```{r}
gapminder_lm_plot("Canada")
gapminder_lm_plot("Canada","year","lifeExp")
gapminder_lm_plot("China","year","gdpPercap")
```

`packageForGapminder` really makes it easier to check the linear relationships between `pop/lifeExp/gdpPercap` and `year` for a gapminder country. Enjoy it!
