---
title: "packageForGapminder"
author: "Lina Qiu"
date: "`r Sys.Date()`"
output: 
   rmarkdown::html_vignette:
   toc: true
   keep_md: true
vignette: >
  %\VignetteIndexEntry{packageForGapminder}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

About packageForGapminder

`packageForGapminder` is a package which makes model pop/lifeExp/gdpPercap VS year for countries in gapminder dataset easier, as well as makes it possible to use only one line code to help you get a intuitive view on how well pop/lifeExp/gdpPercap and year in gapminder dataset fits a linear model.

To install the package:

```{r}
devtools::install_github("LinaQiu/packageForGapminder")
library(packageForGapminder)
```

In this package, we have three functions in total. See below.
* `gapminder_lmfit()`: Fit a linear model to pop/lifeExp/gdpPercap VS year for a country in gapminder dataset. 
* `gapminder_lm_table()`: Create a table for fitted linear model between variables pop/lifeExp/gdpPercap and year in gapminder dataset.
* ```gapminder_lm_plot()`:Draw a plot to show how well pop/lifeExp/gdpPercap and year in gapminder dataset fits a linear model.

Besides, by default, all these three funtions will fit the linear model to data `pop` VS `year` for a gapminder country.

Using `gapminder_lmfit()` to fit linear model to gapminder country data.

```{r}
gapminder_lmfit("Canada")                   ##fit a linear model to pop VS year for "Canada"
gapminder_lmfit("Canada","year","lifeExp")  ##fit a linear model to lifeExp VS year for "Canada"
gapminder_lmfit("China","year","gdpPercap") ##fit a linear model to gdpPercap VS year for "China"
```

Using `gapminder_lm_table()` to get the table which compares the actual pop/lifeExp/gdpPercap values with the predicted values that we get from the linear model.

```{r}
gapminder_lm_table("Canada")
gapminder_lm_table("Canada","year","lifeExp")
gapminder_lm_table("China","year","gdpPercap")
```

Using `gapminder_lm_plot()` to draw a plot to give you an intuitive view on how well a gapminder country data(pop/lifeExp/gdpPercap VS year) fits a linear model.

```{r}
gapminder_lm_plot("Canada")
gapminder_lm_plot("Canada","year","lifeExp")
gapminder_lm_table("China","year","gdpPercap")
```

`packageForGapminder` really makes it easier to check the linear relationships between `pop/lifeExp/gdpPercap` and `year` for a gapminder country. 
